### 2023-05-24 paper/Chapters/Chapter1.tex
OMG it's horrible

As reported by \textcite{duisterhofTartanCalibIterativeWideAngle2022} on
\citedate{duisterhofTartanCalibIterativeWideAngle2022}, the current state-of-the-art
methods
\cite{olsonAprilTagRobustFlexible2011a}
\cite{schopsWhyHaving102020} \cite{krogiusFlexibleLayoutsFiducial2019}
fail on images with high distortion.
\textcite{duisterhofTartanCalibIterativeWideAngle2022} suggested an iterative
the approach of image undistortion and target reprojection, achieving the superior
robustness to the noise than the state-of-the-art methods because the feature
detection is performed on the undistorted image.
% \todo{Probably remove the emphasis on TartanCalib, if I am not going to compare
% with it}

@@

>>>>

As reported by \textcite{duisterhofTartanCalibIterativeWideAngle2022} on
\citedate{duisterhofTartanCalibIterativeWideAngle2022}, the current state-of-the-art
methods
\citep{olsonAprilTagRobustFlexible2011a, schopsWhyHaving102020,
krogiusFlexibleLayoutsFiducial2019}
fail on images with high distortion.
\cite{duisterhofTartanCalibIterativeWideAngle2022} suggested an iterative
the approach of image undistortion and target reprojection, achieving the superior
robustness to the noise than the state-of-the-art methods because the feature
detection is performed on the undistorted image.
% \todo{Probably remove the emphasis on TartanCalib, if I am not going to compare
% with it}

@@

\section{Research objective}\label{sec:research_objective}

The objective of this research is to improve the accuracy of the camera
calibration by finding previously undetected features on the calibration
board \todo{Probably rephrase if I won't compare the actual calibration}. For
that, we formulate the set of research questions:
\begin{itemize}
  \item How to find additional features on the calibration board which were not
    detected by the feature detector?
  \item How to filter out falsely detected features?
    \todo{Add more}
\end{itemize}

### 2023-05-24 paper/Chapters/Chapter2.tex
OMG it's horrible

To achieve a robust calibration, images with repeating patterns are
usually used. The camera
calibration parameters can be found using prior knowledge of the properties of the pattern, such that the pattern invariants hold on
the image. Initially, the chessboard~\citep{OpenCVCameraCalibration, v.douskosAutomaticCalibrationDigital2007} patterns were used
(Fig.~\ref{fig:chessboard}).

Later, ArUco
~\cite{garrido-juradoAutomaticGenerationDetection2014} allowed detecting the
orientation of the pattern, as well as uniquely identifying each located pattern
even under occlusion (Fig. \ref{fig:gboriginal}). Based on ArUco,
ChArUcO~\cite{OpenCVCameraCalibration} (Fig.~\ref{fig:charuco}) and
AprilTag~\cite{olsonAprilTagRobustFlexible2011a} (Fig.~\ref{fig:apriltag}) were
proposed as more robust.

@@

The camera model's choice depends on the camera's physical properties
and the accuracy required. Usually, the parametric models are simpler to use, as
they have only a few parameters and deliver good accuracy. 
The most common are the Double Sphere
model~\cite{usenkoDoubleSphereCamera2018}, the Kannala-Brandt
model~\cite{kannalaGenericCameraModel2006}, and the Field-of-View
model~\cite{devernayStraightLinesHave2001}.
In the ill-posed problem of camera calibration, the common choice
of the camera model is the division
model~\cite{fitzgibbonSimultaneousLinearEstimation2001}.
However, \textcite{schopsWhyHaving102020} show that they tend to have
significantly higher errors than the non-parametric (general) models.
The \textcite{lochmanBabelCalibUniversalApproach2021} suggested a framework for
converting the parameters of a powerful back-projection
\cite{zhangFlexibleNewTechnique2000} model to recover different models' parameters.

@@

Camera calibration using repeating patterns was an important subject for a long
time, for example, \textcite{schaffalitzkyGeometricGroupingRepeated1998} in
\citeyear{schaffalitzkyGeometricGroupingRepeated1998} and
\textcite{zhangFlexibleNewTechnique2000}.

@@

Nevertheless, camera calibration is still an open problem; recently,
multiple new approaches have arisen. 
\textcite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
to camera calibration, with a separate step of converting between camera models.
\textcite{huDeepChArUcoDark2019} used deep learning to detect ChArUcO boards.
Recently, on \citedate{duisterhofTartanCalibIterativeWideAngle2022},
\textcite{duisterhofTartanCalibIterativeWideAngle2022} introduced the iterative
approach to camera calibration, which outperforms the previous state-of-the-art
approaches for wide-angle cameras.

>>>>

To achieve a robust calibration, images with repeating patterns are
usually used. The camera
calibration parameters can be found using prior knowledge of the properties of
the pattern, such that the pattern invariants hold on
the image. Initially, the chessboard~\citep{OpenCVCameraCalibration,
v.douskosAutomaticCalibrationDigital2007} patterns were used
(\cref{fig:chessboard}).

Later, ArUco
~\citep{garrido-juradoAutomaticGenerationDetection2014} (\cref{fig:gboriginal}) and
AprilTag~\citep{olsonAprilTagRobustFlexible2011a} (\cref{fig:apriltag})
allowed detecting the
orientation of the pattern, as well as uniquely identifying each located pattern
even under occlusion. Based on ArUco,
ChArUcO~\citep{OpenCVCameraCalibration} (\cref{fig:charuco}) was
proposed as more robust.

@@

The choice of the camera model depends on the camera's physical properties
and the accuracy required. Usually, the parametric models are simpler to use, as
they have only a few parameters and deliver good accuracy.
The most common are the Double Sphere
model~\citep{usenkoDoubleSphereCamera2018}, the Kannala-Brandt
model~\citep{kannalaGenericCameraModel2006}, and the Field-of-View
model~\citep{devernayStraightLinesHave2001}.
In the ill-posed problem of camera calibration, the common choice
of the camera model is the division
model~\citep{fitzgibbonSimultaneousLinearEstimation2001}.
However, \cite{schopsWhyHaving102020} shows that they tend to have
significantly higher errors than the non-parametric (general) models.
The \cite{lochmanBabelCalibUniversalApproach2021} suggested a framework for
converting the parameters of a powerful back-projection
\cite{zhangFlexibleNewTechnique2000} model to recover different models' parameters.

@@

Camera calibration using repeating patterns was an important subject for a long
time, for example, \cite{schaffalitzkyGeometricGroupingRepeated1998} in
\citeyear{schaffalitzkyGeometricGroupingRepeated1998} and
\cite{zhangFlexibleNewTechnique2000}.

@@

Nevertheless, camera calibration is still an open problem; recently,
multiple new approaches have arisen.
\cite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
to camera calibration, with a separate step of converting between camera models.
\cite{huDeepChArUcoDark2019} used deep learning to detect ChArUcO boards.
Recently, on \citedate{duisterhofTartanCalibIterativeWideAngle2022},
\cite{duisterhofTartanCalibIterativeWideAngle2022} introduced the iterative
approach to camera calibration, which outperforms the previous state-of-the-art
approaches for wide-angle cameras.

\todo{Add the paper about the feature detection}
